Proof No Diamond (3 layers)

### 2024-04-16 lipics-master/comppaths.tex
upload the paper in new LIPlcs format
update the draft of a new figure

@@

Notably, this complexity serves as an upper bound. For instance, solvers like Gurobi are quite adept and usually don't need to evaluate all $2^K$ ReLU configurations to deduce the bounds.
It's worth mentioning that the for loop iterating over neurons $n$ in layer $k$, as seen in line 2, can be executed in parallel. This is feasible because the computation only depends on bounds from preceding layers, not the current layer $k$. This parallelization results in a time complexity of $O(\sum_{i=1}^{\ell} \MILP(N_{i-1},K))$, where $\ell$ denotes the total number of layers and $N_i$ the count of neurons in layers $0, ..., i$.

>>>>

\begin{figure}[h]
	\centering
	\begin{tikzpicture}[>=stealth, node distance=2cm]
		% Input nodes (two types)
		\node[circle, draw, minimum size=0.5cm] (input1) at (-1,0) {$a_0$};
		\node[circle, draw, minimum size=0.5cm] (input2) at (-2,0) {$a_1$};
		\node[circle, draw, minimum size=0.5cm] (input3) at (-4,0) {$a_2$};

		\node[circle, draw, minimum size=0.5cm] (input4) at (-5,0) {$a_3$};
		\node[circle, draw, minimum size=0.5cm] (input5) at (-7,0) {$a_4$};
		\node[circle, draw, minimum size=0.5cm] (input6) at (-8,0) {$a_5$};

		\draw[draw=black, dashed] (-1.5,0) ellipse (1.35 and 0.75);
		\node[below] at (-1.5,-0.75) {$A_{zero}$};

		\draw[draw=black, dashed] (-2,2) ellipse (0.75 and 0.75);
		\node[right] at (-1,2) {$B_{zero}$};

		% Hidden layer nodes

		\node[circle, draw, minimum size=0.5cm, fill=blue!20] (hidden1) at (-2,2) {$n_0$};

		\node[circle, draw, minimum size=0.5cm, fill=blue!20] (hidden2) at (-4,2) {$n_1$};
		\node[circle, draw, minimum size=0.5cm, fill=blue!20] (hidden3) at (-5,2) {$n_2$};

		\node[circle, draw, minimum size=0.5cm, fill=blue!20] (hidden4) at (-7,2) {$n_3$};
		\node[circle, draw, minimum size=0.5cm, fill=blue!20] (hidden5) at (-8,2) {$n_4$};

		\draw[draw=black, dashed] (-4.5,0) ellipse (1.35 and 0.75);
		\node[below] at (-4.5,-0.75) {$A_{pure}$};

		\draw[draw=black, dashed] (-7.5,0) ellipse (1.35 and 0.75);
		\node[below] at (-7.5,-0.75) {$A_{open}$};

		\draw[draw=black, dashed] (-4.5,2) ellipse (1.35 and 0.75);
		\node[left] at (-3.5,3) {$B_{pure}$};

		\draw[draw=black, dashed] (-7.5,2) ellipse (1.35 and 0.75);
		\node[left] at (-8.5,1.5) {$B_{open}$};

		% Output node
		\node[circle, draw, minimum size=0.8cm, fill=red!20] (output) at (-5,4) {$z$};

		% connections

		\draw[->] (input1) -- (hidden1);

		\draw[->] (input3) -- (hidden5);

		\draw[->] (input4) -- (hidden4);

%		% Connect input to hidden layer
		\foreach \i in {3,4} {
			\foreach \h in {3,2} {
				\draw[->] (input\i) -- (hidden\h);
			}
		}

		\foreach \i in {5,6} {
			\foreach \h in {4,5} {
				\draw[->] (input\i) -- (hidden\h);
			}
		}
%		
		% Connect hidden layer to output
		\foreach \h in {2,3,4,5} {
			\draw[->] (hidden\h) -- (output);
		}

%		% Input label
%		\node[left=0.5cm of input1] {Input Layer};
%		% Hidden label
%		\node[right=0.5cm of hidden2] {Hidden Layer};
%		% Output label
%		\node[right=0.5cm of output] {Output Layer};
	\end{tikzpicture}
	\caption{Simple Neural Network with Different Types of Input Nodes}
	\label{fig:neural_network_types_simplified}
\end{figure}

@@

Notably, this complexity serves as an upper bound. For instance, solvers like Gurobi are quite adept and usually do not need to evaluate all $2^K$ ReLU configurations to deduce the bounds.
It's worth mentioning that the for loop iterating over neurons $n$ in layer $k$, as seen in line 2, can be executed in parallel. This is feasible because the computation only depends on bounds from preceding layers, not the current layer $k$. This parallelization results in a time complexity of $O(\sum_{i=1}^{\ell} \MILP(N_{i-1},K))$, where $\ell$ denotes the total number of layers and $N_i$ the count of neurons in layers $0, ..., i$.
